---
title: "Create Graphs"
author: "Julie Le Borgne"
date: "25/05/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---



```{r, echo=FALSE}
library(SMCA)
library(ggpubr)
library(ggplot2)
suppressMessages(library(tidyverse))
library(ggrepel)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
library(tictoc)
```

```{r, echo=FALSE}
data(cheese)

```

On crée une partition des individus sur les villes et des modalités sur les variables. 
#We create a partition of the individuals based on the variable city, and a partition on the categories based on the variables. 

```{r}
Gvar <- partition_variables(cheese)
Gcity <- partition_select (cheese [,3])

#total inertia
Itot <- 1/10*sum(sapply(1:10, function(i) {length(Gvar[[i]])-1}))

```

Nous calculerons 4 types d'analyses différentes : 
- sans contraintes de groupe;
- contrainte de groupe sur les colonnes (groupement des modalités par variable);
- contrainte de groupe sur les rangs (groupement des individus sur les rangs);
- contrainte de groupe sur les rangs et sur les colonnes.

#We will compute 4 types of analysis : 
#- no group constraint, res;
#- a group constraint on the columns (grouping categories by variable), res.var;
#- a group constraint on the rows (grouping the individuals by city), res.city;
#- a group constraint on both the rows and the columns, res.var.city.

We create 3 levels of sparsity on the row constraint c1 and on the column constraint c2 :
- 1 = high sparsity
- sqrt(number of rows)/2 or sqrt(number of columns)/2 = medium sparsity
_ sqrt(number of rows) or sqrt(number of columns) = no sparsity

```{r}
#row constraint
i <- nrow(cheese)
c1 <- c(1, 0.5*sqrt(i), sqrt(i))

#columns constraints
j <- length(unlist(Gvar))
c2 <- c(1, 0.5*sqrt(j), sqrt(j))

```

For each type of analysis, we compute all the combination of the 3 levels of sparsity on the rows and on the columns. 

1)res
L'ensemble des essais sans contraintes de Groupe.
#The analysis without group constraints.
```{r}
tic("analysis 1")
res.1.1 <- SMCA(cheese, c1 = c1[1], c2 = c2[1], n = 10, init="svd")
res.1.2 <- SMCA(cheese, c1 = c1[1], c2 = c2[2], n = 10, init="svd")
res.1.3 <- SMCA(cheese, c1 = c1[1], c2 = c2[3], n = 10, init="svd")
res.2.1 <- SMCA(cheese, c1 = c1[2], c2 = c2[1], n = 10, init="svd")
res.2.2 <- SMCA(cheese, c1 = c1[2], c2 = c2[2], n = 10, init="svd")
res.2.3 <- SMCA(cheese, c1 = c1[2], c2 = c2[3], n = 10, init="svd")
res.3.1 <- SMCA(cheese, c1 = c1[3], c2 = c2[1], n = 10, init="svd")
res.3.2 <- SMCA(cheese, c1 = c1[3], c2 = c2[2], n = 10, init="svd")
res.3.3 <- SMCA(cheese, c1 = c1[3], c2 = c2[3], n = 10, init="svd")
toc()
```


2)res.var
L'ensemble des essais avec Groupement sur les variables.
#The analysis with variable group constraint and without group constraint on the observations (row).
```{r}
tic("analysis 2")
res.1.1.var <- SMCA(cheese, c1 = c1[1], c2 = c2[1], Gcol = Gvar, n = 10, init="svd")
res.1.2.var <- SMCA(cheese, c1 = c1[1], c2 = c2[2], Gcol = Gvar, n = 10, init="svd")
res.1.3.var <- SMCA(cheese, c1 = c1[1], c2 = c2[3], Gcol = Gvar, n = 10, init="svd")
res.2.1.var <- SMCA(cheese, c1 = c1[2], c2 = c2[1], Gcol = Gvar, n = 10, init="svd")
res.2.2.var <- SMCA(cheese, c1 = c1[2], c2 = c2[2], Gcol = Gvar, n = 10, init="svd")
res.2.3.var <- SMCA(cheese, c1 = c1[2], c2 = c2[3], Gcol = Gvar, n = 10, init="svd")
res.3.1.var <- SMCA(cheese, c1 = c1[3], c2 = c2[1], Gcol = Gvar, n = 10, init="svd")
res.3.2.var <- SMCA(cheese, c1 = c1[3], c2 = c2[2], Gcol = Gvar, n = 10, init="svd")
toc()
```

3)res.city
L'ensemble des essais avec un groupement sur les villes.
#The analysis with group constraint on the rows (city) and without group constraint on the columns (variable).
```{r}
tic("analysis 3")
res.1.1.city <- SMCA(cheese[,-3], c1 = c1[1], c2 = c2[1], Grow = Gcity, n = 10, init="svd")
res.1.2.city <- SMCA(cheese[,-3], c1 = c1[1], c2 = c2[2], Grow = Gcity, n = 10, init="svd")
res.1.3.city <- SMCA(cheese[,-3], c1 = c1[1], c2 = c2[3], Grow = Gcity, n = 10, init="svd")
res.2.1.city <- SMCA(cheese[,-3], c1 = c1[2], c2 = c2[1], Grow = Gcity, n = 10, init="svd")
res.2.2.city <- SMCA(cheese[,-3], c1 = c1[2], c2 = c2[2], Grow = Gcity, n = 10, init="svd")
res.2.3.city <- SMCA(cheese[,-3], c1 = c1[2], c2 = c2[3], Grow = Gcity, n = 10, init="svd")
res.3.1.city <- SMCA(cheese[,-3], c1 = c1[3], c2 = c2[1], Grow = Gcity, n = 10, init="svd")
res.3.2.city <- SMCA(cheese[,-3], c1 = c1[3], c2 = c2[2], Grow = Gcity, n = 10, init="svd")
toc()
```

4)res.city.var
L'ensemble des essais avec un groupement sur les villes et sur les variables.
#The analysis with group constraint on the rows (city) and on the columns (variable).
```{r}

Gvar2 <- partition_variables(cheese[,-3])
tic("analysis 4")
res.1.1.city.var <- SMCA(cheese[,-3], c1 = c1[1], c2 = c2[1], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.1.2.city.var <- SMCA(cheese[,-3], c1 = c1[1], c2 = c2[2], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.1.3.city.var <- SMCA(cheese[,-3], c1 = c1[1], c2 = c2[3], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.2.1.city.var <- SMCA(cheese[,-3], c1 = c1[2], c2 = c2[1], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.2.2.city.var <- SMCA(cheese[,-3], c1 = c1[2], c2 = c2[2], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.2.3.city.var <- SMCA(cheese[,-3], c1 = c1[2], c2 = c2[3], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.3.1.city.var <- SMCA(cheese[,-3], c1 = c1[3], c2 = c2[1], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
res.3.2.city.var <- SMCA(cheese[,-3], c1 = c1[3], c2 = c2[2], Gcol = Gvar2, Grow = Gcity, n = 10, init="svd")
toc()
```

# Screeplots
#tests of the screeplots
```{r, echo=FALSE}
p1 <- screeplot_new(res.1.1.city, title = "1.1.city")
p2 <- screeplot_new(res.2.2.city, title = "2.2.city")
p3 <- screeplot_new(res.3.3, title = "3.3")

ggarrange(p1, p2, p3)
```


#print all the screeplots of a type of analysis on the same plot
```{r, echo=FALSE}
res <- data.frame(res.1.1$eig$eigenvalue/Itot,
                  res.1.2$eig$eigenvalue/Itot,
                  res.1.3$eig$eigenvalue/Itot,
                  res.2.1$eig$eigenvalue/Itot,
                  res.2.2$eig$eigenvalue/Itot,
                  res.2.3$eig$eigenvalue/Itot,
                  res.3.1$eig$eigenvalue/Itot,
                  res.3.2$eig$eigenvalue/Itot,
                  res.3.3$eig$eigenvalue/Itot)

names1 <- sapply(1:ncol(res), function(i) {substr(colnames(res)[i], 5, 7)})
screeplot_cum(res, names.res = names1, title = "Screeplots without group constraint")


res2 <- data.frame(res.1.1.city$eig$eigenvalue/Itot,
                  res.1.2.city$eig$eigenvalue/Itot,
                  res.1.3.city$eig$eigenvalue/Itot,
                  res.2.1.city$eig$eigenvalue/Itot,
                  res.2.2.city$eig$eigenvalue/Itot,
                  res.2.3.city$eig$eigenvalue/Itot,
                  res.3.1.city$eig$eigenvalue/Itot,
                  res.3.2.city$eig$eigenvalue/Itot,
                  res.3.3$eig$eigenvalue/Itot)

names2 <- c(sapply(1:(ncol(res2)-1), function(i) {substr(colnames(res2)[i], 5, 12)}), "3.3")
screeplot_cum(res2, names.res = names2, title = "Screeplots with city constraint")

res3 <- data.frame(res.1.1.var$eig$eigenvalue/Itot,
                  res.1.2.var$eig$eigenvalue/Itot,
                  res.1.3.var$eig$eigenvalue/Itot,
                  res.2.1.var$eig$eigenvalue/Itot,
                  res.2.2.var$eig$eigenvalue/Itot,
                  res.2.3.var$eig$eigenvalue/Itot,
                  res.3.1.var$eig$eigenvalue/Itot,
                  res.3.2.var$eig$eigenvalue/Itot,
                  res.3.3$eig$eigenvalue/Itot)

names3 <- c(sapply(1:(ncol(res3)-1), function(i) {substr(colnames(res3)[i], 5, 12)}), "3.3")
screeplot_cum(res3, names.res = names3, title = "Screeplots with variable constraint")


res4 <- data.frame(res.1.1.city.var$eig$eigenvalue/Itot,
                  res.1.2.city.var$eig$eigenvalue/Itot,
                  res.1.3.city.var$eig$eigenvalue/Itot,
                  res.2.1.city.var$eig$eigenvalue/Itot,
                  res.2.2.city.var$eig$eigenvalue/Itot,
                  res.2.3.city.var$eig$eigenvalue/Itot,
                  res.3.1.city.var$eig$eigenvalue/Itot,
                  res.3.2.city.var$eig$eigenvalue/Itot,
                  res.3.3$eig$eigenvalue/Itot)

names4 <- c(sapply(1:(ncol(res4)-1), function(i) {substr(colnames(res4)[i], 5, 12)}), "3.3")
screeplot_cum(res4, names.res = names4, title = "Screeplots with city and variable constraint")


ggsave("ScreeCum_cityvar",
       plot = screeplot_cum(res4, names.res = names4, title = "Screeplots with city and variable constraint"),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")

```

# Individuals factor map
#plot of the individuals factor map of res
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.3")

ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T)

# ggsave("IndFactorMap",
#        plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T),
#        path = "C:/Users/hub/Documents/figures_cheese_20200603",
#        device = "pdf")
```

#plot of the individuals factor map of res.var
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T)
# ggsave("IndFactorMap_var",
#        plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T),
#        path = "C:/Users/hub/Documents/figures_cheese_20200603",
#        device = "pdf")
```

#plot of the individuals factor map of res.city
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.city, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T)

ggsave("IndFactorMap_city",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```

#plot of the individuals factor map of res.city.var
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.city.var, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, habillage = 3)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T)

ggsave("IndFactorMap_var_city",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3, common.legend = T),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```

# Variables factor maps

#plot of the variables factor map of res
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)

ggsave("VarFactorMap",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```

#plot of the variables factor map of res.var
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
ggsave("VarFactorMap_var",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```

#plot of the variables factor map of res.city
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.city, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
ggsave("VarFactorMap_city",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```

#plot of the variables factor map of res.city.var
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.city.var, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "var", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.3")

# ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
ggsave("VarFactorMap_cityvar",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```

# Categories factor map

#plot of the categories factor map of res
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.3")

ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
# ggsave("CatFactorMap",
#        plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
#        path = "C:/Users/hub/Documents/figures_cheese_20200603",
#        device = "pdf")
```
#plot of the categories factor map of res.var
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.var, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.var, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.var, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.3")

ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
# ggsave("CatFactorMap_var",
#        plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
#        path = "C:/Users/hub/Documents/figures_cheese_20200603",
#        device = "pdf")
```

#plot of the categories factor map of res.city
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.city, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.city, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.city, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.city, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.city, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.city, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.city, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.city, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.3")

ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
ggsave("CatFactorMap_city",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```


#plot of the categories factor map of res.city.var
```{r, echo=FALSE}
p1.1 <- plot_SMCA(res.1.1.city.var, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("1.1")
p1.2 <- plot_SMCA(res.1.2.city.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.2")
p1.3 <- plot_SMCA(res.1.3.city.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("1.3")
p2.1 <- plot_SMCA(res.2.1.city.var, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("2.1")
p2.2 <- plot_SMCA(res.2.2.city.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.2")
p2.3 <- plot_SMCA(res.2.3.city.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("2.3")
p3.1 <- plot_SMCA(res.3.1.city.var, choix = "mod", aff.noms = T)+ theme(legend.position = "none")+ ggtitle("3.1")
p3.2 <- plot_SMCA(res.3.2.city.var, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.2")
p3.3 <- plot_SMCA(res.3.3, choix = "mod")+ theme(legend.position = "none")+ ggtitle("3.3")

ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3)
ggsave("CatFactorMap_cityvar",
       plot = ggarrange(p1.1, p1.2, p1.3, p2.1, p2.2, p2.3, p3.1, p3.2, p3.3),
       path = "C:/Users/hub/Documents/figures_cheese_20200603",
       device = "pdf")
```


```{r}
# plot_SMCA(res.smca1, habillage = 3)
# plot_SMCA(res.smca1, habillage = 3, axes = c(3,4))
# 
# plot_SMCA(res.smca2, habillage = 3)
# plot_SMCA(res.smca2, habillage = 3, axes = c(3,4))
# 
# plot_SMCA(res.smca1, choix = "var", aff.noms = T) + theme(legend.position = "none")
# plot_SMCA(res.smca1, choix = "var", aff.noms = T,  axes = c(3,4)) + theme(legend.position = "none")
# 
# plot_SMCA(res.smca2, choix = "var", aff.noms = T) + theme(legend.position = "none")
# plot_SMCA(res.smca2, choix = "var", aff.noms = T,  axes = c(3,4)) + theme(legend.position = "none")
# 
# plot_SMCA(res.smca1, choix = "mod", aff.noms = T) + theme(legend.position = "none")
# plot_SMCA(res.smca1, choix = "mod", aff.noms = T,  axes = c(3,4)) + theme(legend.position = "none")
# 
# plot_SMCA(res.smca2, choix = "mod", aff.noms = T) + theme(legend.position = "none")
# plot_SMCA(res.smca2, choix = "mod", aff.noms = T,  axes = c(3,4)) + theme(legend.position = "none")
```
